Trends of SDR in Thessaloniki 

### 2022-10-13 Article.Rmd
Commit 2022-10-13 13:17

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all values to the mean Sun and Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

>>>>

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute values to the mean Sun and Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

<!-- data selection -->
We select all data with $\text{SZA} < `r 90-MIN_ELEVA`^\circ$, in order to avoid measurements near the horizon. Where the signal is very low and the disturbances more frequent.
<!-- avoid obstacles -->
Similar, we exclude values data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. Where, due to some obstructions around the site (hills and buildings) the Sun, were not visible by the instruments. . At 
those cases.
